\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage[usenames]{color}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in
\hypersetup{pdfborder = 0 0 0}
\raggedright

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
    \begin{changemargin}{-0.05in}{-0.05in}
        \vspace*{-8pt}
        \hrulefill \\
        \vspace*{-2pt}
    \end{changemargin}
}

\newcommand{\header}[1]{
    \begin{changemargin}{-0.5in}{-0.5in}
        \scshape{#1}\\
    \lineover
    \end{changemargin}
}

\newcommand{\contact}[4]{
    \begin{changemargin}{-0.5in}{-0.5in}
        \begin{center}
            {\Large \scshape {#1}}\\ \smallskip
            {#2}\\ \smallskip
            {#3}\\ \smallskip
            {#4}\smallskip
        \end{center}
    \end{changemargin}
}

\newenvironment{body} {
    \vspace*{-16pt}
    \begin{changemargin}{-0.25in}{-0.5in}
  }
    {\end{changemargin}
}

\newcommand{\school}[4]{
    \textbf{#1} \hfill \emph{#2\\}
    #3\\
    #4\\
}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Apurva Dey}{https://apurvadey.github.io}{apurvadey51@gmail.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Objective
\header{Summary}

\begin{body}
    \vspace{14pt}
Apurva has completed her 2nd year undergraduate in Computer Science from Banasthali Vidyapith. She is seeking internship opportunities in software startups. She is very hard working and is always eager to learn more and contribute to ongoing projects.


\begin{itemize} \itemsep -0pt
    \item Fast learner who is open to learn new technologies.
    \item Developed problem-solving and analytical skills.
    \item Resourceful and efficient, with a talent for improvisation.
    \item Strong written and verbal English competency.
\end{itemize}

\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
    \vspace{14pt}
    \textbf{B.Tech Computer Science }{} \hfill \emph{July 2017 - May 2021}{} \\
    \emph{Banasthali Vidyapith}, Rajasthan{} \\
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Courses and Projects}

\begin{body}
    \vspace{14pt}
    \textbf{Udacity}: \emph{Frontend Development} \hfill \emph{Fed 2018 - May, 2018}\\
    Web basics with HTML, CSS and JavaScript.
    \vspace*{-4pt}
    \vspace{14pt}

    \textbf{edX}: \emph{IoT} \hfill \emph{Dec, 2018 - Present}\\
    Ongoing course related to Internet of Things
    \vspace*{-4pt}

    \vspace{14pt}
    
    \textbf{Harvard}: \emph{CS50} \hfill \emph{Dec 2018 - Present}\\
    Ongoing course for Computer Science
    \vspace*{-4pt}
    \vspace{14pt}
\end{body}

\smallskip

% \newpage{} % uncomment this line if you want to force a new page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Skills}

\begin{body}
    \vspace{14pt}
    \textbf{Programming Languages:}{} C/C++, HTML, CSS, Python(beginner), JavaScript(beginner)\\
    \textbf{Database:}{} Oracle\\
    \textbf{Version Control:}{} Git\\
    \textbf{Operating System:}{} Linux, Windows\\
    \textbf{Foreign Language:}{} German (beginner)\\
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Links
\header{Important links}

\begin{body}
    \vspace{14pt}
    \textbf{github} :  \url{https://github.com/apurvadey}\\
    \smallskip
    \textbf{linkedin} :  \url{https://www.linkedin.com/in/apurva-dey-9a0b24175/}\\
    \smallskip
    \textbf{twitter} :  \url{https://twitter.com/apurvadey1}\\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Leadership
\header{Leadership Activities & Achievements}

\begin{body}
    \vspace{14pt}
    \textbf{Event Co-ordinator} : Opening and closing events of physical education, (Banasthali Vidyapith) \hfill {} \emph{July 2018-May 2019}\\
    \smallskip
    \textbf{Remarkable Performance, XIIth Board Toppers List (90.8 percent)}: (DPS, Ranchi) \hfill{} \emph{2016}\\
    \textbf{LARA Appreciate, Xth Board ICSE Toppers (94.2 percent)}: (Loreto Convent, Ranchi) \hfill{} \emph{2014}\\
    \textbf{House Captain} : (Loreto Convent, Ranchi) \hfill{} \emph{March 2013- March 2014}\\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
\header{Blog}

\begin{body}
    \vspace{14pt}
    Personal Blog \textbf{Web blog on my learnings as a computer science undergraduate} \emph{ https://apurvadey.github.io}\\
    \smallskip
\end{body}

\smallskip

\end{document}
