\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}

\renewcommand{\familydefault}{\sfdefault}

\begin{document}

% ==== Header ====
\begin{center}
    {\LARGE \textbf{Vinit Kumar}}\\
    \small \href{mailto:mail@vinitkumar.me}{mail@vinitkumar.me} | +91 8554862210 | 
    \href{https://github.com/vinitkumar}{GitHub} | 
    \href{https://www.linkedin.com/in/vinitatlinkedin/}{LinkedIn}
\end{center}

% ==== Skills ====
\section*{Skills}
\textbf{Programming:} Go, Python, JavaScript, TypeScript, Ruby on Rails, PHP, C \\
\textbf{DevOps:} AWS, Google Cloud Platform, DigitalOcean, CI/CD (GitHub Actions, Bitbucket Pipelines) \\
\textbf{Web Development:} Django, FastAPI, Laravel, Express.js, Ruby On Rails, PostgreSQL, MySQL, MongoDB, Redis, Elasticsearch, React \\
\textbf{Testing:} Unit Testing, TDD (Pytest, Vitest, PHPUnit)

% ==== Experience ====
\section*{Experience}

\textbf{Principal Engineer, Scalefusion} \hfill Pune, India \\
\textit{Nov 2024 – Present}  
\begin{itemize}[leftmargin=0.15in]
    \item Lead architecture and development of large-scale distributed systems using Go, solving complex engineering challenges with precision.
    \item Design and optimize high-performance back-end systems, ensuring seamless scalability and reliability.
    \item Collaborate cross-functionally to improve system efficiency, implementing solutions that improve performance.
    \item Develop and maintain core services in Go, TypeScript, and Ruby on Rails, ensuring high availability and fault tolerance.
    \item Optimize cloud infrastructure and CI/CD pipelines, improving deployment efficiency and reducing downtime.
\end{itemize}

\textbf{Staff Software Engineer, KidsKonnect (prev SocialSchools B.V.)} \hfill Pune, India \\
\textit{Feb 2013 – Nov 2024}  
\begin{itemize}[leftmargin=0.15in]
    \item Designed and implemented a highly scalable distributed multitenant CMS in Python, managing more than 2,500 domains and improving page load speeds by 35\%.
    \item Led development of an Enrollment Form \& CRM system, reducing onboarding time by 40\% and increasing customer sign-ups by 25\%.
    \item Built an internal monitoring tool, reducing downtime incidents by 30\% through real-time uptime tracking.
    \item Developed a Go-based analytics tracker, reducing the data processing time by 50\% and improving the efficiency of the system.
    \item Created a Celery \& RabbitMQ-based distributed task queue, reducing job execution time by 45\% and handling 3x more concurrent tasks.
    \item Optimized cloud infrastructure, reducing AWS costs by 20\% through auto-scaling and right-sizing instances.
    \item Spearheaded performance improvements, cutting API response times from 400ms to 120ms, improving user experience.
    \item Led containerization efforts (Docker, Kubernetes), enabling seamless local development across different OS environments.
    \item Mentored junior developers on Django and React, fostering a culture of best practices and continuous learning.
\end{itemize}

\textbf{Software Developer, Open Source} \hfill Remote \\
\textit{2010 – Present}  
\begin{itemize}[leftmargin=0.15in]
    \item Django CMS Fellow at Django CMS, contributing to the core and plugin ecosystem (Paid Fellowship).
    \item Principal author of \texttt{json2xml}, used by Engineers from Google, Amazon, and NASA.
    \item Developed a chat-bot in C with a lightweight NLP engine.
    \item Created \texttt{node-twitter}, a Twitter clone using Node.js and MongoDB.
    \item Designed "white paper," a top-10 Jekyll theme with thousands of downloads.
\end{itemize}

% ==== Education ====
\section*{Education}
\textbf{Birla Institute of Technology, Mesra} \hfill \textit{July 2008 – April 2012} \\
\textit{Bachelor of Engineering (Specialization: Python programming, Linux, C)}  
\begin{itemize}[leftmargin=0.15in]
    \item \textbf{Graduation Project:} Applied genetic algorithms to predict sedimentation rates in reservoirs in India.
\end{itemize}

% ==== Recommendations ====
\section*{Recommendations}
\textbf{Available on:} \href{https://www.linkedin.com/in/vinitatlinkedin/details/recommendations/}{LinkedIn} |
\href{https://github.com/vinitkumar}{GitHub} 

\end{document}