\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
    \begin{changemargin}{-0.05in}{-0.05in}
        \vspace*{-8pt}
        \hrulefill \\
        \vspace*{-2pt}
    \end{changemargin}
}

\newcommand{\header}[1]{
    \begin{changemargin}{-0.5in}{-0.5in}
        \scshape{#1}\\
    \lineover
    \end{changemargin}
}

\newcommand{\contact}[4]{
    \begin{changemargin}{-0.5in}{-0.5in}
        \begin{center}
            {\Large \scshape {#1}}\\ \smallskip
            {#2}\\ \smallskip
            {#3}\\ \smallskip
            {#4}\smallskip
        \end{center}
    \end{changemargin}
}

\newenvironment{body} {
    \vspace*{-16pt}
    \begin{changemargin}{-0.25in}{-0.5in}
  }
    {\end{changemargin}
}

\newcommand{\school}[4]{
    \textbf{#1} \hfill \emph{#2\\}
    #3\\
    #4\\
}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Vinit Kumar}{https://vinitkumar.me}{vinit1414.08@bitmesra.ac.in}{+91-8554862210}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Objective
\header{Summary}

\begin{body}
    \vspace{14pt}
  Vinit is a Senior Engineer at Socialschools B.V(https://www.socialschools.nl/). His expertise lies in writing scalable backend systems in Python, Django, Golang, Node.js and React. He occasionally dabbles with iOS and Android development too.

He enjoys solving difficult problems, debugging and coming up with simple solutions.

At Socialschools, he has worked on APIs, performance, scaling and security of the complete application. With over 5 years of experience in Python/Django, he is able to rapidly build features and debug nasty bugs.
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
    \vspace{14pt}
    \textbf{B.E Civil Engineering }{} \hfill \emph{July 2008 - Sep 2012}{} \\
    \emph{Birla Institute of Technology}, Mesra{} \\
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Career History}

\begin{body}
    \vspace{14pt}
    \textbf{Senior Software Engineer}, \emph{Social Schools B.V., Pune} \hfill \emph{Feb 2013 - Present}\\
    Working on APIs, performance, scaling and security of the complete application suite.
    \vspace*{-4pt}

    \vspace{14pt}
    \textbf{App development Consultant}, \emph{gadgetizor.com and digitizor.com} \hfill \emph{Summer 2011 - Jan 2013}\\
    \vspace*{-4pt}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Worked on the design and scaling of WordPress based high traffic sites.
    \end{itemize}

    \textbf {JavaScript Developer}, \emph{Worked on a E-Commerce based Chrome Extension and extension listed on Coderwall.com http://coderwall.com/api} \hfill \emph{Sep 2012 - Jan 2012}\\
    \vspace*{-4pt}
    \begin{itemize} \itemsep -0pt
        \item Wrote a chrome extension integrating Facebook APIs and E-Commerce site Flipkart.
    \end{itemize}
\end{body}

\smallskip

% \newpage{} % uncomment this line if you want to force a new page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Skills}

\begin{body}
    \vspace{14pt}
    \emph{\textbf{Programming Languages:}}{} Python, JavaScript/Node.js, Go, C, Obj-C, Rust, Tex, Java\\
    \emph{\textbf{Frontend Frameworks:}}{} React, Angular, Backbone\\
    \emph{\textbf{Database:}}{} PostgreSQL, MySQL, MongoDB, SQLite\\
    \emph{\textbf{Version Control:}}{} Git, Mercurial\\
    \emph{\textbf{Backend Frameworks:}}{} Django, Flask, Express.js\\
    \emph{\textbf{Mobile Development:}}{} Android, iOS(minor experience), React Native\\
    \emph{\textbf{Operating Systems:}}{} macOS, Linux, Windows\\
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Links
\header{Important links}

\begin{body}
    \vspace{14pt}
    \textbf{Github} : https://github.com/vinitkumar \hfill{}\\
    \smallskip
    \textbf{Linkedin} : https://www.linkedin.com/in/vinitatlinkedin/ \hfill{}\\
    \smallskip
    \textbf{Twitter} : https://twitter.com/vinitkme \hfill{}\\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Leadership
\header{Leadership Activities}

\begin{body}
    \vspace{14pt}
    \textbf{Administrator, In-Charge} : Linux User Group, (Bit Mesra) \hfill {} \emph{June 2011 - May 2012}\\
    \smallskip
    \textbf{Administrator} : Web and DC server, (Bit Mesra) \hfill{} \emph{June 2011- May 2012}\\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
\header{Blog}

\begin{body}
    \vspace{14pt}
    Gotchacode \textbf{Tech-blog covering topics related to web and Open Source.} \emph{ https://gotchacode.com}\\
    \smallskip
\end{body}

\smallskip

\end{document}
